
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{enumitem}
\usepackage{hyperref}

\title{Annexure A: Permanent Placement Commercials and Detailed Scope of Work}
\date{}

\begin{document}

\maketitle

\section*{1. Services}
Anantam HR will provide permanent placement recruitment services to the Client, including candidate sourcing, screening, and interview coordination. Reference checks are available at the Client's discretion for an additional fee.

\section*{2. Charges}
The fee is 8.33\% of the candidate's annual CTC. Background verification (BGV), GST, and other specific requirements are additional.

\section*{3. Replacement Guarantee}

If a candidate placed by \textbf{Anantam HR Ltd} resigns within the applicable replacement period from their joining date, the Client will be entitled to a \textbf{replacement candidate at no additional cost}.

The replacement guarantee period will be applicable as follows:

\begin{itemize}
\item Up to 3 LPA CTC: 1 Month replacement period
\item Up to 9 LPA CTC: 2 Months replacement period
\item Above 9 LPA CTC: 3 Months replacement period
\end{itemize}

To avail this replacement guarantee, the Client must notify Anantam HR Ltd in writing within 7 days of the candidate?s resignation, along with relevant details of the resignation and reference to the original job requisition.

Upon receiving such notification, Anantam HR Ltd will make reasonable efforts to provide a suitable replacement within a reasonable timeframe.

This guarantee is limited to a \textbf{maximum of 3} replacements per original placement and shall not apply in cases where the candidate is terminated by the Client, or where the resignation arises due to changes made to the originally agreed role, responsibilities, location, or compensation structure.

The replacement period will be calculated from the start date of the first candidate placed and will not reset or extend for any subsequent replacement candidates.

\section*{4. Payment Terms}

This agreement is valid from the execution date until termination. New terms can be mutually agreed upon. Fees exclude taxes.

The Client is responsible for GST and other applicable taxes.

Anantam HR Ltd will invoice the Client for taxes and expenses and provide necessary tax documents.

50\% payment is due within 30 days of the invoice date, and the remaining 50\% is due within the next 15 days.

Payments must be made via bank transfer to Anantam HR Ltd's account.

Overdue payments incur a 2\% monthly interest.

Payment details and tax certificates should be sent to:
\href{mailto:manila.bhatia@anantamhr.com}{manila.bhatia@anantamhr.com}

\section*{5. Detailed Scope of Work}

\textbf{Our Responsibilities:}

\begin{itemize}
\item Obtain the candidate's permission before presenting them to the Client.
\item Present only potentially suitable candidates for short-listing and assessment.
\item Inform the Client of any known inaccuracies or incompleteness in the candidate's information.
\item Arrange interviews with selected candidates.
\item Refrain from poaching from the Client during this contract.
\end{itemize}

\textbf{Client's Responsibilities:}

\begin{itemize}
\item Provide written confirmation of the required services.
\item Provide complete and accurate position details including job descriptions, requirements, desired attributes, duties and KPIs.
\item Within 48 working hours of receiving a candidate's resume, either schedule a meeting or provide feedback.
\item Immediately notify Anantam HR Ltd of interview outcomes or employment decisions.
\item Ensure the candidate qualification \& suitability.
\end{itemize}

\section*{6. Duplicate Profile Clause}

Anantam HR Ltd will source and share profiles as per agreed requirements.

If the Client identifies a duplicate profile, they must provide verifiable proof within 48 hours including the original email or document.

\section*{7. DPD 2023 Compliance Clause}

\begin{itemize}
\item Anantam HR Ltd will adhere to Data Protection Directive (DPD 2023) regulations in handling data.
\item Both parties will keep records of data for 12 months for audits and compliance.
\end{itemize}

\bigskip
This Annexure may be executed in counterparts, each deemed an original.

\bigskip
\textbf{For Client}

\vspace{2cm}

\noindent\rule{6cm}{0.4pt}  
Authorized Signatory

\end{document}
