\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{sectsty}
\usepackage{enumitem}
\usepackage{hyperref}

% Modern Color Palette
\definecolor{primary}{HTML}{007bff}
\definecolor{secondary}{HTML}{6c757d}
\definecolor{lightgray}{HTML}{f8f9fa}
\definecolor{darkgray}{HTML}{343a40}

% Modern Font for Headings
\sectionfont{\fontsize{14}{17}\selectfont\color{primary}\bfseries}
\subsectionfont{\fontsize{12}{15}\selectfont\color{secondary}\bfseries}

% Custom List Environment
\newenvironment{customlist}
  {\begin{itemize}[leftmargin=*, label=$\bullet$, itemsep=0.5em]}
  {\end{itemize}}

\title{\textbf{\color{primary} Annexure A: Permanent Placement Commercials and Detailed Scope of Work}}
\date{}

\begin{document}
\maketitle

\noindent\textbf{SHIV SHAKTI LAMINATES PRIVATE LIMITED}\\
Udhana Magdalla Road-Surat\\[1em]

\noindent\textbf{Thank you for the opportunity to serve your organization.}\\[0.5em]
\noindent\textit{Anantam HR is dedicated to conducting business with integrity and a strong ethical foundation.}\\[1em]

\noindent\textbf{\color{secondary} Our Guiding Principles}\\[0.5em]
\noindent At Anantam Placement Consultancy, we follow a set of guiding principles that reflect our commitment to fairness, integrity, and service quality:

\begin{enumerate}[label=\arabic{enumi}.]
    \item \textbf{Services}\\
        Anantam HR will provide permanent placement recruitment services to the Client, including candidate sourcing, screening, and interview coordination. Reference checks are available at the Client's discretion for an additional fee.
    \item \textbf{Charges}\\
        The fee is \texttt{7\%} of the candidate's annual CTC. Background verification (BGV), GST, and other specific requirements are additional.
    \item \textbf{Replacement Guarantee}\\
        If a candidate resigns within \texttt{90} days of their start date, the Client is entitled to a replacement at no extra cost. To claim a replacement, the Client must notify Anantam HR in writing within 7 days of the resignation, including details of the resignation and the original job requisition. Anantam HR will provide a suitable replacement within a reasonable time. This guarantee is limited to three replacements per original placement and excludes terminations by the Client or resignations due to changes in the original role or remuneration. The \texttt{90} day replacement period applies from the first candidate's start date and does not reset with subsequent replacements.
    \item \textbf{Payment Terms}\\
        This agreement is valid from the execution date until termination. New terms can be mutually agreed upon. Fees exclude taxes. The Client is responsible for GST and other applicable taxes. Anantam HR will invoice the Client for taxes and expenses and provide necessary tax documents. 50\% payment is due within \texttt{15} days of the invoice date, and the remaining 50\% is due within \texttt{30} days. Payments must be made via bank transfer to Anantam HR?s account. Overdue payments incur a 2\% monthly interest. Payments are subject to applicable tax deductions. Payment must be by bank transfer only. The Client is responsible for any tax rate changes. Payment details and tax certificates should be sent to \href{mailto:[manila.bhatia@anantamhr.com]}{manila.bhatia@anantamhr.com}.
    \item \textbf{Detailed Scope of Work}\\
        \subsection*{\color{secondary} Our Responsibilities: Anantam HR will take reasonable steps to:}
        \begin{customlist}
            \item Obtain the candidate's permission before presenting them to the Client.
            \item Present only potentially suitable candidates for short-listing and assessment.
            \item Inform the Client of any known inaccuracies or incompleteness in the candidate's information.
            \item Arrange interviews with selected candidates.
            \item Refrain from poaching from the Client during this contract.
        \end{customlist}
        \subsection*{\color{secondary} Client's Responsibilities: The Client will:}
        \begin{customlist}
            \item Provide written confirmation of the required services.
            \item Provide complete and accurate position details, including job descriptions, requirements, desired attributes, duties, and KPIs (if available).
            \item Immediately notify Anantam HR of:
            \begin{itemize}[leftmargin=*, label=$\circ$, itemsep=0.25em]
                \item Interview outcomes
                \item Any offer or acceptance of an offer to our candidate
                \item The employment or engagement of our candidate.
            \end{itemize}
            \item Ensure the candidate qualification \& suitability.
        \end{customlist}
    \item \textbf{Duplicate Profile Clause}\\
        Anantam HR will source and share profiles as per agreed requirements. If the Client identifies a duplicate profile, they must provide verifiable proof, including a screenshot of the original email or document with the date and sender details.
    \item \textbf{DPD 2023 Compliance Clause}\\
        \begin{customlist}
            \item Anantam HR will adhere to Data Protection Directive (DPD 2023) regulations in handling data. All personal information will be managed in compliance with applicable privacy laws.
            \item Both parties will keep records of data for 12 months for audits and compliance.
        \end{customlist}
\end{enumerate}

\noindent\textbf{This Annexure may be executed in counterparts, each deemed an original.}\\[1em]

\noindent\textbf{\color{secondary} Signatures}\\[0.5em]
\noindent\textbf{For Anantam HR:}

\end{document}